A Memory-Bounded, Deterministic and Terminating Semantics for the Synchronous Programming Language~\CEU

### 2018-04-14 03-semantics.tex
Minor rephrasing in Section 3

The use of qualifier ``irreducible'' in Definition~\ref{def.x.Hnst} is
justified by Proposition~\ref{prop.x.irr-nst-i}.  The proposition
establishes that if a finite number of applications of~$\nst$ results in an
irreducible description, then that can only occur exactly once, at some
specific number~$i$.  The proof of the lemma follows directly from the
definition of~$\nst$ by contradiction on the hypothesis that there is
such~$k\ne{i}$.

@@

Theorem~\ref{thm.x.term-nst-*} establishes that a finite (possibly zero)
number of~$\nst$ transitions eventually lead to a nested-irreducible
description.  The proof is by induction on the structure of programs
(members of set~$P$) and uses Lemma~\ref{lem.x.props-nst-i} and
Assumption~\ref{ass.x.syn-rest}.

@@

  More formally, $\pot(p,e)=\pot'(\bcast(p,e))$ where~$\pot'$ is an
  auxiliary function that counts the number of reachable~$\ceu{\EmitInt}$
  expressions in the program resulting from the broadcast of event~$e$
  to~$p$.

>>>>

The use of qualifier ``irreducible'' in Definition~\ref{def.x.Hnst} is
justified by Proposition~\ref{prop.x.irr-nst-i}.  The proposition
establishes that if a finite number of applications of~$\nst$ results in an
irreducible description, then that occurs exactly once, at some specific
number~$i$.  The proof of the lemma follows directly from the definition
of~$\nst$ by contradiction on the hypothesis that there is such~$k\ne{i}$.

@@

Theorem~\ref{thm.x.term-nst-*} establishes that a finite (possibly zero)
number of~$\nst$ transitions eventually leads to a nested-irreducible
description.  The proof is by induction on the structure of programs
(members of set~$P$) and uses Lemma~\ref{lem.x.props-nst-i} and
Assumption~\ref{ass.x.syn-rest}.

@@

  More formally, $\pot(p,e)=\pot'(\bcast(p,e))$ where~$\pot'$ is an
  auxiliary function that counts the maximum number of
  reachable~$\ceu{\EmitInt}$ expressions in the program resulting from the
  broadcast of event~$e$ to~$p$.
